Reasonably Programmable Literal Notation

### 2018-06-28 icfp18/syntax-icfp18.tex
formatting tweaks required by ACM

\PassOptionsToPackage{svgnames,dvipsnames,svgnames}{xcolor}
%% For double-blind review submission
% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=false,printccs=false,printacmref=false}
\documentclass[acmsmall]{acmart}
% \documentclass[sigplan,review,10pt,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
% \documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission
%\documentclass[acmlarge,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[acmlarge]{acmart}\settopmatter{}

@@

\makeatletter
\renewcommand{\subsubsection}{%
  \@startsection{subsubsection}{3}%
  {\z@}{1ex \@plus .2ex \@minus .2ex}{-1em}%
  {\normalfont\normalsize\bfseries}%
}
\makeatother

@@

\makeatletter\if@ACM@journal\makeatother
%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2018}
\acmMonth{9}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\else\makeatother
%% Conference information (used by SIGPLAN proceedings format)
%% Supplied to authors by publisher for camera-ready submission
\acmConference[ICFP'18]{International Conference on Functional Programming}{September 23--29, 2018}{St. Louis, MO, USA}
\acmYear{2018}
\acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}
\fi

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission
% \setcopyright{none}             %% For review submission
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\copyrightyear{2017}           %% If different from \acmYear

@@

%% Author with single affiliation.
\author{Cyrus Omar}
\authornote{The majority of this research was performed while the first author attended Carnegie Mellon University.}          %% \authornote is optional;
                                        %% can be repeated if necessary
\affiliation{
  \institution{University of Chicago}            %% \institution is required
  \city{Chicago}
  \state{IL}
  % \country{USA}
}
\email{comar@cs.uchicago.edu}          %% \email is recommended
% \affiliation{
%   \institution{Carnegie Mellon University}           %% \institution is required
%   \city{Pittsburgh}
%   \state{PA}
%   % \country{USA}
% }

%% Author with two affiliations and emails.
\author{Jonathan Aldrich}
\affiliation{
  \institution{Carnegie Mellon University}           %% \institution is required
  \city{Pittsburgh}
  \state{PA}
  % \country{USA}
}
\email{jonathan.aldrich@cs.cmu.edu}         %% \email is recommended

@@

%% Keywords
%% comma separated list
% \keywords{keyword1, keyword2, keyword3}  %% \keywords is optional

@@

\begin{figure}[h]
\vspace{-9px}
\begin{lstlisting}
  fun heading first_name = SURL<xml><h1>Hello, {[EURLfirst_nameSURL]}!</h1></xml>EURL
  val body = SURL<xml><body>{EURLheading "World"SURL} ...</body></xml>EURL
\end{lstlisting}
\vspace{-3px}
\caption{HTML literals with support for splicing at two types are built primitively into Ur/Web \cite{conf/popl/Chlipala15}.}
\label{fig:urweb}
\vspace{-10px}
\end{figure}

>>>>

\PassOptionsToPackage{svgnames,dvipsnames,svgnames}{xcolor}
%% For double-blind review submission
% \documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=false,printccs=false,printacmref=false}
\documentclass[acmsmall,screen]{acmart}
% \documentclass[sigplan,review,10pt,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
% \documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission
%\documentclass[acmlarge,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[acmlarge]{acmart}\settopmatter{}

@@

\makeatletter
\renewcommand{\subsubsection}{%
  \@startsection{subsubsection}{3}%
  {\z@}{1ex \@plus .2ex \@minus .2ex}{-1em}%
  {\sffamily\normalsize\bfseries\maybe@addperiod}%
}

\newcommand{\maybe@addperiod}[1]{%
  #1\@addpunct{.}%
}
\makeatother

@@

% \makeatletter\if@ACM@journal\makeatother
% %% Journal information (used by PACMPL format)
% %% Supplied to authors by publisher for camera-ready submission
% \acmJournal{PACMPL}
% \acmVolume{1}
% \acmNumber{1}
% \acmArticle{1}
% \acmYear{2018}
% \acmMonth{9}
% \acmDOI{10.1145/nnnnnnn.nnnnnnn}
% \startPage{1}
% \else\makeatother
% %% Conference information (used by SIGPLAN proceedings format)
% %% Supplied to authors by publisher for camera-ready submission
% \acmConference[ICFP'18]{International Conference on Functional Programming}{September 23--29, 2018}{St. Louis, MO, USA}
% \acmYear{2018}
% \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
% \acmDOI{10.1145/nnnnnnn.nnnnnnn}
% \startPage{1}
% \fi

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission
% \setcopyright{none}             %% For review submission
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%%% The following is specific to ICFP'18 and the paper
%%% 'Reasonably Programmable Literal Notation'
%%% by Cyrus Omar and Jonathan Aldrich.
%%%
\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3234629}
\acmYear{2018}
\copyrightyear{2018}
\acmJournal{PACMPL}
\acmVolume{2}
\acmNumber{ICFP}
\acmArticle{40}
\acmMonth{9}

@@

%% Author with single affiliation.
\author{Cyrus Omar}
\authornote{The majority of this research was performed while the first author attended Carnegie Mellon University.}          %% \authornote is optional;
                                        %% can be repeated if necessary
\affiliation{
  \institution{University of Chicago}            %% \institution is required
  \city{Chicago}
  \state{IL}
  \country{USA}
}
\email{comar@cs.uchicago.edu}          %% \email is recommended
% \affiliation{
%   \institution{Carnegie Mellon University}           %% \institution is required
%   \city{Pittsburgh}
%   \state{PA}
%   % \country{USA}
% }

%% Author with two affiliations and emails.
\author{Jonathan Aldrich}
\affiliation{
  \institution{Carnegie Mellon University}           %% \institution is required
  \city{Pittsburgh}
  \state{PA}
  \country{USA}
}
\email{jonathan.aldrich@cs.cmu.edu}         %% \email is recommended

@@

%% Keywords
%% comma separated list
\keywords{parsing, macro systems, hygiene, type systems, pattern matching}  %% \keywords is optional

@@

\begin{figure}[h]
% \vspace{-9px}
\begin{lstlisting}
  fun heading first_name = SURL<xml><h1>Hello, {[EURLfirst_nameSURL]}!</h1></xml>EURL
  val body = SURL<xml><body>{EURLheading "World"SURL} ...</body></xml>EURL
\end{lstlisting}
\vspace{-3px}
\caption{HTML literals with support for splicing at two types are built primitively into Ur/Web \cite{conf/popl/Chlipala15}.}
\label{fig:urweb}
\vspace{-10px}
\end{figure}
